Software Citation Principles

### 2016-03-25 sc-principles/software-citation-principles.tex
Metadata section

AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}
\acmnote{ CodeMeta? }

>>>>

Producing detailed specifications and recommendations for possible metadata standards to support software citation was not within the scope of this working group. However some discussion on the topic did occur and there is significant interest in the wider community to produce standards for describing research software.

Notable examples of community efforts around metadata include the AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta}
